\section{Formulating closure relationships for higher-order moments in terms of lower-order moments}
\label{sec:formulating-closure-relationships-for-higher-order-moments-in-terms-of-lower-order-moments}

This section delves into the derivation of closure relationships for crucial higher-order moments
employed within the \gls{CLUBB} parameterization.

Our focus here lies on achieving closure for the following terms:
\begin{itemize}
    \item $\wpfour$: The fourth-order moment of up-/downdrafts,
    \item $\wptwothlp$: the so-called flux of flux,
    \item $\wpthlptwo$: the flux of variance,
    \item $\wprtpthlp$: and the flux of covariance.
\end{itemize}
Note, that $\wprtpthlp$ is just listed for completeness,
we already found the formula for this moment (see~\cref{eq:w_prime_theta_l_prime_bar}).
Closure, in this context,
refers to expressing these higher-order moments completely in terms of known quantities,
typically lower-order moments that are directly prognosed by the model.
The approach to derive those formulas is based on
the previously established expressions for the \gls{pdf} parameters (equations~\eqref{eq:alpha_solved} to~\eqref{eq:r_r_t_theta_l}).
By substituting those derived \gls{pdf} parameter expressions
into the relevant equations for the higher-order moments (equations~\eqref{eq:wp4_div_wp2_2} to~\eqref{eq:wprtpthlp_div_wp2_thp2_rt2}),
we find the desired closure relationships.

We first present the equation for the third moment of $\theta_l'$, $\thlpthree$.
This expression is derived by dimensionalizing \cref{eq:Sk_hat_thl_beta},
which relates the skewness of $\theta_l$ to the skewness of $w$ and other model parameters.
\begin{align}
    \label{eq:thlp3_beta}
    \thlpthree
    &= \frac{(1-\delta \lambda_{w \theta})(1-\delta \lambda_\theta)}{\tswfact^2 (1-\delta \lambda_w)^2}
    \frac{\wpthree}{\left( \wptwo \right)^2}
    \thlptwo \;
    \wpthlp
    \left(\beta + (1-\beta)
    \frac{(1-\delta \lambda_{w \theta})^2}{1-\tsw^2 (1-\delta \lambda_w)(1-\delta \lambda_\theta)}
    \frac{\left(\wpthlp\right)^2}{\wptwo \; \thlptwo}\right).
\end{align}
While the scalar third moments (e.g., $\thlpthree$) may not directly participate
in solving the prognostic equations within \gls{CLUBB},
they hold an indirect yet crucial role in shaping cloud properties within atmospheric simulations.
This influence is coming from the connection between the \gls{pdf} and the cloud formation.

Cumulus cloud formation mostly occurs at the edges,
or \enquote{tails} of the \gls{pdf} for a specific variable.
These tails represent regions where the probability of encountering extreme values of the variable is relatively higher.
As the relative \enquote{width} of the normal distribution representing $w$ increases ($\tsw$),
the magnitude of $\thlpthree$ also grows (refer to~\cref{eq:thlp3_beta} for details).
In simpler terms, a larger value of $\thlpthree$ corresponds to a broader \gls{pdf} for the up-/downdraft variable.
This broader \gls{pdf} deviates more significantly from a double delta function,
which is a construct with two spikes at zero.

Unlike the scalar third moment,
$\wpfour$ does not depend on the thermodynamic scalar moments (such as $\thlpthree$).
Consequently, it is independent of the parameter $\beta$.
To derive the explicit formula for $\wpfour$,
we can substitute the previously stated expressions for $\widehat{w}_1$ (\cref{eq:w1_solved})
and $\widehat{w}_2$ (\cref{eq:w2_solved}) into \cref{eq:wp4_div_wp2_2}.
\begin{align}
    \label{eq:wp4_div_wp2_2_solved}
    \frac{1}{\tswfact^2} \frac{(1-\delta)}{(1-\delta \lambda_w)^2} \frac{\wpfour}{\left(\wptwo\right)^2}
    &= 3 \frac{\tsw^4}{\tswfact^2} + 6 \frac{\tsw^2}{\tswfact} + 1 \nonumber\\
    &+ \widehat{Sk}_w^2 + \frac{1}{\tswfact^2} \frac{(1-\delta)}{(1-\delta \lambda_w)^2} \delta 3 \lambda_w^2,
\end{align}
leading to
\begin{align}
    \label{eq:wp4}
    \wpfour
    &= \left(\wptwo\right)^2
    \frac{(1-\delta \lambda_w)^2}{(1-\delta)}
    \left(3 \tsw^4 + 6 \tswfact \tsw^2 + \tswfact^2\right) \nonumber\\
    &+ \frac{1}{\tswfact} \frac{1}{(1-\delta \lambda_w)}
    \frac{\left(\wpthree\right)^2}{\wptwo} \nonumber\\
    &+ \delta 3 \lambda_w^2 \left(\wptwo\right)^2.
\end{align}
As observed with $\wpfour$,
$\wptwothlp$ displays independence from the parameter $\beta$
within the context of the chosen \gls{pdf}.

To proceed, we can substitute the previously derived expressions for
$\widehat{w}_1$ (\cref{eq:w1_solved}), $\widehat{w}_2$ (\cref{eq:w2_solved}),
$\widehat{Sk}_w$ (\cref{eq:sk_hat_w_nondim}),
$\tilde{\theta}_{l1}$ (\cref{eq:thl1_tilde_solved}),
and $\tilde{\theta}_{l2}$ (\cref{eq:thl2_tilde_solved}) into \cref{eq:wp2thlp_div_wp2thl2}.
This substitution process will yield an explicit formula for $\wptwothlp$ that solely relies on known quantities,
such as the prognostic moments directly calculated by the model.
\begin{align}
    \label{eq:wp2thlp_sk_w_solved}
    \frac{1}{\tswfact} \frac{(1-\delta)^{1/2}}{(1-\delta \lambda_w) (1-\delta \lambda_\theta)^{1/2}} \frac{\wptwothlp}{\wptwo \left(\thlptwo \right)^{1/2}}
    &= \widehat{c}_{w\theta_l} \widehat{Sk}_w,
\end{align}
and
\begin{align}
    \label{eq:wp2thlp_solved}
    \wptwothlp
    &= \frac{1}{\tswfact} \frac{1 - \delta \lambda_{w\theta}}{1-\delta \lambda_w} \frac{\wpthree}{\wptwo} \wpthlp.
\end{align}
$\wpthlptwo$ depends explicitly on $Sk_{\theta_l}$.
Substituting \cref{eq:w1_solved} - \cref{eq:sigma_tilde_theta2_solved}
into \cref{eq:wprtpthlp_div_wp2_thp2_rt2} yields
\begin{align}
    \label{eq:wpthlp2_sk_w_solved}
    \frac{1}{\tswfact^{1/2}} \frac{(1-\delta)^{1/2}}{(1-\delta \lambda_w)^{1/2} (1-\delta \lambda_\theta)} \frac{\wpthlptwo}{\left(\wptwo\right)^{1/2} \thlptwo}
    &= \frac{2}{3} \widehat{c}_{w\theta_l}^2 \widehat{Sk}_w + \frac{1}{3} \frac{ \widehat{Sk}_{\theta_l} } {\widehat{c}_{w\theta_l}},
\end{align}
and
\begin{align}
    \label{eq:wpthlp2_solved}
    \wpthlptwo
    &= \frac{2}{3} \frac{(1-\delta \lambda_{w \theta})^2}{(1-\delta \lambda_w)^2} \frac{1}{\tswfact^2} \frac{\wpthree}{\left(\wptwo \right)^2} \left(\wpthlp \right)^2 \nonumber\\
    &+ \frac{1}{3} \frac{(1-\delta \lambda_w)}{(1-\delta \lambda_{w \theta})} \tswfact \frac{\wptwo \; \thlpthree}{\wpthlp}.
\end{align}